Exploring the linear separablity of syntactic and semantic information in BERT embeddings

### 2022-06-09 paper/paper.tex
fixing typos

The original dataset does not include CCG Tags, but \citealp{pmbData} utilized CCG parser to produce CCG tags. We follow a similar procedure to apply a CCG parser \citep{ccg_tagger} to develop word-level CCG tags. Once we obtain both CCG tags and semantics tags for the dataset, we can perform syntactic and semantics probing task as desired.%Fill this in
 %Do we drop anything or do any other pre-processing that I missed here?

>>>>

The original dataset does not include CCG tags. \citealp{pmbData} utilized CCG parser to produce CCG tags. We followed a similar procedure and applied a CCG parser \citep{ccg_tagger} to develop word-level CCG tags. Once we obtain both CCG tags and semantics tags for the dataset, we can perform syntactic and semantics probing task as desired.%Fill this in
 %Do we drop anything or do any other pre-processing that I missed here?
